---
title: "Question1"
author: "Zander Prinsloo"
date: "5/24/2021"
output:
  pdf_document: default
  html_document: default
---


```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5)
options(dplyr.summarise.inform=F)

#Load Packages
if(!require(pacman))(install.packages("pacman")) # in case someone has not installed `pacman`
library(pacman)
p_load(tidyverse, lubridate, xtable, purrr, ggsci)

# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

# Source Functions
list.files('Question1/code/', full.names = T, recursive = T) %>% 
    as.list() %>% 
    walk(~source(.))

# Data

```

```{r}
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
# Source Question 1's code too ()for plot_order function) - note ..// here means go up one level from current folder
list.files('..//Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
# Data loading:

# Import Data
Loc <- "/Users/zanderprinsloo/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Desktop – MacBookPro’s MacBook Pro/Academic/Postgraduate/Masters/Modules/Data Science/Test/20065124/data/Movies/"
df_movies <- read_csv(paste0(Loc, "Movies.csv"),
                      col_names = T,
                      col_types = cols())

```


# Task

I will seek to prove that movie critics were not a near perfect prediction of a film'a popularity and profitability amongst audiences in the mid-2000s. In order to do that I use the **Movies.csv** data set given to me by my friend at *Mr Video*. I will try to disprove her claims using plots throughout. 

# Claim 1 

She claims that: 
*:if a movie had a rating of more than 80% on Rotten Tomatoes, audiences would rate it above 85% every time."*

The barplot below clearly shows that my friend's claim is false. For the films that Rotten Tomatoes rated above 80, an overwhelming majority was not rated above 85 by audiences. 

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Caption Here \\label{Figure1}", fig.ext = 'png', fig.height = 6, fig.width = 7}
g1 <- Barplot1_Q1(df = df_movies, 
            title = "Rotten Tomatoes is Rotten", 
            subtitle = "RT is a bad predictor of what audiences love", 
            caption = "Thank you to Mr Video for the data", 
            Xlab = "Rotten Tomatoes Rating", 
            Ylab = "Number of Films in Each Class", 
            xaxis_size = 10)

g1
```


# Claim 2

The second claim is that *"Disney films may not have the highest grossing numbers, but they’ve always been the most profitable of all the leading studios."*

I will show that they have not always been the most profitable out of the leading studios. 


There is one film called `r df_movies %>% filter(Profitability>60) %>% select(Film)` that has a very high profitability of `r df_movies %>% filter(Profitability>60) %>% select(Profitability)`. It is an outlier that will be excluded from the plot along with any missing values of profitability or studios. 
```{r}
df_movies %>% 
    filter(Profitability>60)
```
In \ref{Figure2} we see that Disney is not clearly the most profitable film. While it's median is very close to Fox, Sony, and Summit, it's upper quintile is substantially lower than Summit. Note also that Disney is being pulled up by an outlier, `r df_movies %>% filter(Profitability>20 & Profitability <60) %>% select(Film)`

```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "Boxplot Comparing Disney's Profitability \\label{Figure2}", fig.ext = 'png', fig.height = 6, fig.width = 7}

g2 <- Boxplot_Q1(df = df_movies, 
                 Title = "Profitability of Leading Studios", 
                 Subtitle = "Disney vs Others", 
                 Caption = "Note: \n Thank you to Mr Video for the data", 
                 Ylab = "Studios", 
                 Xlab = "Profitability of Films")
g2

```
If we remove this outlier, we get \ref{Figure3}. It shows that Disney is an average performer in terms of Profitability. It's median is lwoer than Fox, and its upper quintile appears lower than Fox, Sony, Summit, and Universal Studios.
```{r Figure3,  warning =  FALSE, fig.align = 'center', fig.cap = "Boxplot Comparing Disney's Profitability \\label{Figure3}", fig.ext = 'png', fig.height = 6, fig.width = 7}

df_g2 <- g2$data
g2 %+%
    subset(df_g2, Profitability<20)

```

Therefore, it is not clear that Disney is indeed more profitable. The plots indicate that there are a number of studios that are more profitable and more consistent. 



# Claim 3

The third claim is that *"Audiences are always drawn to the highest grossing films"*. She goes further to claim that the correlation between world wwide grossing numbers and audience scores would be near 80%. 

<!-- The correlation between these two variables is `r as.matrix(df_movies %>% select("Audience  score %", "Worldwide Gross")) ` -->



```{r}
df_use <- bind_rows(df_movies %>% 
    select("Audience  score %", "Worldwide Gross") %>% 
        mutate(Type = "Audience and Gross Relationship") %>% 
    summarise(AudienceScore = as.numeric(`Audience  score %`), 
              WorldWideGross = as.numeric(`Worldwide Gross`), 
              Type), 
    tibble(AudienceScore = seq(from = 30, to = 90, length = nrow(df_movies)), 
              WorldWideGross = seq(from = 100, to = 600, length = nrow(df_movies)))) %>% 
    mutate(Type = ifelse(is.na(Type), "Linear Relationship", Type))

```

Note that \ref{Figure4} gives the relationship between world wide gross and audience rating. The linear line is shows what a strong correlation would look like. However, the actual line plot of the relationship between world wide gross and audience scores is much more jagged and sporadic. There is not a clear linear relationship and correlation. This means that the third claim also appears false.

```{r Figure4,  warning =  FALSE, fig.align = 'center', fig.cap = "Jagged Line Plot of Gross and Rating \\label{Figure4}", fig.ext = 'png', fig.height = 6, fig.width = 7}

g3 <- Lineplot_Q1(df = df_movies, 
                  Title = "Line Plot - Relationship Between World Wide Gross and Audience Scores",
                  Subtitle = "Compared to a strong correlation", 
                  Caption = "Note: \n Thank you to Mr Video for the data", 
                  Ylab = "World Wide Gross", 
                  Xlab = "Audience Ratings")
g3
```







